The \dealii Library, Version 9.5

### 2023-07-27 9.5/paper.tex
computing acks

W.~Bangerth and T.~Heister were partially
supported by the Computational Infrastructure for Geodynamics initiative
(CIG), through the National Science Foundation (NSF) under Award
No.~EAR-1550901 and The University of California -- Davis.

@@

>>>>

W.~Bangerth and T.~Heister were partially
supported by the Computational Infrastructure for Geodynamics initiative
(CIG), through the National Science Foundation (NSF) under Award
No.~EAR-1550901 and EAR-2149126 via The University of California -- Davis.

@@

Clemson University is acknowledged for generous allotment of compute time on Palmetto cluster.

The authors acknowledge the Texas Advanced Computing Center (TACC) at The University of Texas at Austin for providing HPC resources that have contributed to the research results reported within this paper. \url{http://www.tacc.utexas.edu}

This work used the Extreme Science and Engineering Discovery Environment (XSEDE), which is supported by National Science Foundation grant number ACI-1053575 access through the CIG Science Gateway and Community Codes for the Geodynamics Community MCA08X011 allocation.
